Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data

### 2024-12-06 paper/paper.tex
minor

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Ensuring fairness in AI systems is crucial, but auditing these systems often requires sensitive data, which raises security and privacy concerns. To address this, we introduce a framework that utilizes Differentially Private synthetic data for fairness evaluations. This approach allows auditors to assess AI systems without exposing sensitive information. Through experiments on datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data. Our results ...
\end{abstract}

@@

\begin{definition}[R\'enyi Differential Privacy (RDP)]\label{def:rdp}
Let $P_{\mathbf{X}}$ denote the probability distribution induced by the random vector $\mathbf{X}$. A randomized mechanism $M$ satisfies $(\alpha,\gamma)$-RDP for $\alpha \geq 1$ and $\gamma \geq 1$ if, for all databases $\db_1 \sim \db_2$, we have
\[
D_\alpha(P_{M(\db_1)} \Vert P_{M(\db_2)}) \leq \gamma
\]
where $D_\alpha(P_1 \Vert P_2)$ is the R\'enyi divergence\cite{van2014renyi,van2010renyi,li2016renyi} of order $\alpha$ between probability distributions $P_1,P_2$ over $x$:
\[
D_\alpha(P_1 \Vert P_2) := \frac{1}{\alpha - 1} \text{log} \int {P_1(x)}^\alpha {P_2(x)}^{1-\alpha} \text{d}x
\]
\end{definition}

@@

In a perfect world where all correlation information is to be preserved, we may wish to make a completely connected graph. However, this is intractable as the complexity of the problem would skyrocket. Furthermore, algorithms for Markov random field favor graphs with specific shapes, such as trees.

@@

\begin{algorithm}
\caption{something something}
\label{alg:heuristic}
\begin{algorithmic}[1]
\STATE Initialize $x \gets 0$
\STATE Initialize $y \gets 1$
\FOR{$i \gets 1$ to $n$}
    \IF{$i$ is even}
        \STATE $x \gets x + i$
    \ELSE
        \STATE $y \gets y \times i$
    \ENDIF
\ENDFOR
\RETURN $x + y$
\end{algorithmic}
\end{algorithm}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Ensuring fairness in AI systems is crucial, but auditing these systems often requires sensitive data, which raises security and privacy concerns. To address this, we introduce a framework that utilizes Differentially Private synthetic data for fairness evaluations. This approach allows auditors to assess AI systems without exposing sensitive information. Through experiments on datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data. Our results ... (to be continued)
\end{abstract}

@@

\begin{definition}[R\'enyi Differential Privacy (RDP)]\label{def:rdp}
Let $P_{\mathbf{X}}$ denote the probability distribution induced by the random vector $\mathbf{X}$. A randomized mechanism $M$ satisfies $(\alpha,\gamma)$-RDP for $\alpha \geq 1$ and $\gamma \geq 1$ if, for all databases $\db_1 \sim \db_2$, we have
\[
D_\alpha(P_{M(\db_1)} \Vert P_{M(\db_2)}) \leq \gamma
\]
where $D_\alpha(P_1 \Vert P_2)$ is the R\'enyi divergence\cite{van2014renyi,van2010renyi,li2016renyi} of order $\alpha$ between probability distributions $P_1,P_2$ over $x$
\[
D_\alpha(P_1 \Vert P_2) := \frac{1}{\alpha - 1} \text{log} \int {P_1(x)}^\alpha {P_2(x)}^{1-\alpha} \text{d}x
\]
\end{definition}

@@

In a perfect world where all correlation information is to be preserved, we may wish to make a complete graph. However, this is intractable as the complexity of the problem would skyrocket. Furthermore, algorithms for Markov random field favor graphs with specific shapes, such as trees.

@@

% \begin{algorithm}
% \caption{something something}
% \label{alg:heuristic}
% \begin{algorithmic}[1]
% \STATE Initialize $x \gets 0$
% \STATE Initialize $y \gets 1$
% \FOR{$i \gets 1$ to $n$}
%     \IF{$i$ is even}
%         \STATE $x \gets x + i$
%     \ELSE
%         \STATE $y \gets y \times i$
%     \ENDIF
% \ENDFOR
% \RETURN $x + y$
% \end{algorithmic}
% \end{algorithm}
